---
title: "RMarkdown-Homework-ODDAnalysis_Assignment2"
author: "Leyla Yigit"
date: "31 Ekim 2018"
output: html_document
---


```{r }

# Load the package to the session
library(readr)
library(tidyverse)
library(scales)
library(stringr)
library(zoo)

```




```{r DOWNOAD RAW DATA}
#Download Raw Data
# Create a temporary file
tmp<-tempfile(fileext=".xlsx")
# Download file from repository to the temp file
download.file("https://github.com/MEF-BDA503/pj18-Leyla.Yigit/blob/master/AssignmentWeek2/odd_retail_sales_2016_10.xlsx?raw=true",mode="wb",destfile=tmp)
# Read that excel file using readxl package's read_excel function. You might need to adjust the parameters (skip, col_names) according to your raw file's format.
raw_data<-readxl::read_excel(tmp,skip=7,col_names=FALSE)
# Remove the temp file
file.remove(tmp)
```

## Remove the last two rows because they are irrelevant (total and empty rows)


```{r pressure}
plot(pressure)
raw_data <- raw_data %>% slice(-c(48,49))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Let's see our raw data

```{r RAW DATA CHECK}
head(raw_data)
```


## Make Data Civilized

```{r MAKE CIVILIZED DATA}
#In order to make the data standardized and workable we need to define column names and remove NA values for this example. 
#Please use the same column names in your examples also.
# Use the same column names in your data.
colnames(raw_data) <- c("MARKA","oto_yerli","oto_ithal","oto_toplam","ticari_yerli","ticari_ithal","ticari_toplam","toplam_yerli","toplam_ithal","toplam_toplam")
# Now we replace NA values with 0 and label the time period with year and month, so when we merge the data we won't be confused.
car_data_oct_16<- raw_data %>% mutate_if(is.numeric,funs(ifelse(is.na(.),0,.))) %>% mutate(year=2016,month=10)

print(car_data_oct_16,width=Inf)
```


## Save Your Civilized Data

```{r CIVILIZED DATA SAVE}
#One of the best methods is to save your data to an RDS or RData file. 
#The difference is RDS can hold only one object but RData can hold many. Since we have only one data frame here we will go with RDS.
# Save an object to a file
saveRDS(car_data_oct_16, file = "car_data_oct_16.rds")
```


##                                                                                       ANALYSIS
## --1--- a list of total sales of brands with both automobile and commercial vehicle sales ordered in decreasing total sales.

```{r ANALYSIS}
car_data_oct_16 %>% 
  filter(oto_toplam > 0 & ticari_toplam > 0) %>%
  select(MARKA,toplam_toplam) %>%
  arrange(desc(toplam_toplam))
```

** Analysis Result: VOLKSWAGEN has the highest number of sales; on the other hand SSANGYONG has the lowest sales number **


#Calculate the mean of sales numbers 
```{r car_data_oct_16}
car_data_oct_16 %>%
  summarise(sales_num_mean=mean(toplam_toplam),dom_sales_num_maen=mean(toplam_yerli),imp_sales_num_mean=mean(toplam_ithal),com_sales_num_mean=mean(ticari_ithal),oto_sales_num_mean=mean(oto_ithal))
```

** Analysis Result: As a result,in 2016,10 customers prefer import cars more than domestic ones.From this import cars, sales of indiviual cars is higher than commercial car sales **


## --2---Get the VOLKSWAGEN sales numbers, compare commercial and car types. 
```{r VOLKSWAGEN}
car_data_oct_16 %>% 
  filter(MARKA=='VOLKSWAGEN' ) %>% 
  select(MARKA,(toplam_toplam),(toplam_yerli)  ,(toplam_ithal))%>%
  arrange (desc(sum(toplam_toplam)))
```

** Analysis Result:VOLKSWAGEN is an import car and has 12229 number of sales 2016,10 **


## --3---Get the car names sales number is equal to 0 and order car name asc
```{r arrange}
car_data_oct_16 %>%
  filter(toplam_toplam==0) %>%
  select(MARKA,toplam_toplam) %>%
  arrange( MARKA)
```


** Analysis Result:There are 7 car brand have 0 number of sales in 2016,10 **

## --4---Get the car names and numbers sales number more than 2000 and how many of this number domestic or import and order sales number desc.
```{r group_by}
car_data_oct_16 %>%
  group_by(MARKA) %>%
  filter(sum(toplam_toplam)>2000) %>%
  select(MARKA,toplam_ithal,toplam_yerli,toplam_toplam) %>%
  arrange(desc(toplam_toplam))
```

## --5---Compare cars and commercial cars, which brand has the highest sales. In that highest group, do customers prefer domestic or import
```{r car_data_oct_16_comp }
car_data_oct_16_comp <-
  car_data_oct_16 %>%
 # group_by(MARKA)%>%
  #aggregate( by=list(toplam_yerli,toplam_ithal,toplam_toplam), FUN=sum)
  summarise(dip_toplam=sum(toplam_toplam),ticari_toplam=sum(ticari_toplam),oto_toplam=sum(oto_toplam))
  #mutate(dip_toplam = sum(toplam_toplam))

car_data_oct_16_comp

```

**Analysis Result:Indıvidual car type is more preffred by customers than commercial ones.**










